Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-04-18 analysis/feature-importance.Rmd

```{r fi-hr-ale, dev = c("png", "pdf")}
fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) *
  theme_pubr(base_size = 12) *
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

>>>>

```{r fi-hr-ale, dev = c("png", "pdf")}
fi_ale_hr_buffer2$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) &
  theme_pubr(base_size = 12) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_hr_buffer2_gs20$plot(
  features = df_wavelengths_from_hr$class,
  ncol = 2
) &
  theme_pubr(base_size = 12) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r fi-vi-ale, dev = c("png", "pdf")}
fi_ale_vi_buffer2$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) &
  theme_pubr(base_size = 12) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

@@

```{r}
fi_ale_vi_buffer2_gs20$plot(
  features = paste0("bf2_", df_wavelengths_from_indices_label$class),
  ncol = 2
) &
  theme_pubr(base_size = 12) &
  theme(
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13)
  )
```

### 2020-04-18 docs/00-manuscripts/ieee/performance-best-per-learner.tex

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR-NRI & SVM & Car & 27.98 & 19.19 \\ 
  2 & HR-NRI & RF & Car & 31.08 & 17.09 \\ 
  3 & NRI-VI & XGBOOST & Relief & 32.10 & 17.73 \\ 
  4 & NRI & Ridge-CV & No Filter & 32.97 & 7.24 \\ 
  5 & HR & Lasso-CV & No Filter & 45.96 & 18.35 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & NRI & SVM & Info Gain & 27.99 & 19.15 \\ 
  2 & NRI & RF & Car & 30.77 & 16.86 \\ 
  3 & VI & Lasso-MBO & No Filter & 31.01 & 14.71 \\ 
  4 & HR-NRI-VI & XGBoost & Borda & 31.05 & 17.01 \\ 
  5 & NRI & Ridge-MBO & No Filter & 31.16 & 15.03 \\ 
   \hline
\end{tabular}
}
\end{table}

### 2020-04-18 docs/00-manuscripts/ieee/performance-svm-single-plot.tex

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Single fold performances for learner SVM on the HR dataset without using a filter.} 
\label{tab:svm-single-fold-perf}
\begin{tabular}{rlr}
  \hline
 & Plot & RMSE \\ 
  \hline
1 & Luiando & 9.00 \\ 
  2 & Laukiz1 & 21.17 \\ 
  3 & Laukiz2 & 54.26 \\ 
  4 & Oiartzun & 28.05 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Test fold performances for learner SVM on the HR dataset without using a filter. For each row, the model was trained on observations from fold all other plots and tested on the observations of the given plot.} 
\label{tab:svm-single-fold-perf}
\begin{tabular}{rlr}
  \hline
 & Plot & RMSE \\ 
  \hline
1 & Luiando & 21.17 \\ 
  2 & Laukiz1 & 28.05 \\ 
  3 & Laukiz2 & 9.00 \\ 
  4 & Oiartzun & 54.26 \\ 
   \hline
\end{tabular}
\end{table}
